---
title: "RIA final project - Evolution of Japan’s trade flows after signing the ASEAN+1 agreement on Comprehensive Economic-Partnership in 2008."
author: "Kateryna Hanina"
format: html
---

Countries (11): Brunei (BRN), Cambodia (KHM), Indonesia (IDN), Laos (LAO), Malaysia (MYS), Myanmar (MMR), Philippines (PHL), Singapore (SGP), Thailand (THA), Vietnam (VNM), Japan (JPN).

# General

```{r}
library(tidyverse)
library(fixest) # perform estimations with multiple fixed-effects
library(stargazer)
library(flextable)
library(huxtable)
library(modelsummary)
```

# Custom formulas

```{r}
# To get lagged values in function of CONSECUTIVE observations (here years)
tlag <- function(x, n = 1L, along_with, default = NA) { 
  if (!is.numeric(n) | (length(n)>1)) stop("n must be a numeric of length one")
  index <- match(along_with - n, along_with, incomparables = NA)
  out <- x[index]
  if (!is.na(default)) out[which(is.na(index))] <- default
  out
}
```

```{r}
# To get lead values in function of CONSECUTIVE observations (here years)
tlead <- function(x, n = 1L, along_with, default = NA) { 
  if (!is.numeric(n) | (length(n)>1)) stop("n must be a numeric of length one")
  index <- match(along_with + n, along_with, incomparables = NA)
  out <- x[index]
  if (!is.na(default)) out[which(is.na(index))] <- default
  out
}
```


# Data

```{r}
data_asean_raw <- read.csv("./Gravity_csv_V202211/Gravity_V202211.csv")
```

## General modifications

```{r}
#Select only countries and columns we need
#remove non-existing countries after they started existing in different form (+Singapore independence since 1965)
#remove tech variables
data_asean_selected <- data_asean_raw %>%
  select(c(year, country_id_o, country_id_d, iso3_o, iso3_d, country_exists_o, country_exists_d, dist, comlang_off, comlang_ethno, comcol, col45, comleg_pretrans, comleg_posttrans, comrelig, col_dep_end_conflict, gdp_o, gdp_d, gatt_o, gatt_d, wto_o, wto_d, rta_type, tradeflow_comtrade_d)) %>%
  filter(year >= 1965 & country_exists_o == 1 & country_exists_d == 1) %>%
  select(-c(country_id_o, country_id_d, country_exists_o, country_exists_d))
```

```{r}
#set rta_type and trade flows to 0 if NA
data_asean_selected <- data_asean_selected %>%
  mutate(rta_type = coalesce(rta_type, 0),
         tradeflow_comtrade_d = coalesce(tradeflow_comtrade_d, 0))
```

```{r}
#create new columns:
#general presence in either GATT or WTO by origin and destination
#general dummy for presence of any RTA for all countries
#dummy for presence in either GATT or WTO if both countries are members of it
data_asean_selected <- data_asean_selected %>%
  mutate(gatt_wto_o = case_when((gatt_o == 1 | wto_o == 1) ~ 1, TRUE ~ 0),
         gatt_wto_d = case_when((gatt_d == 1 | wto_d == 1) ~ 1, TRUE ~ 0),
         rta = if_else(rta_type == 0, 0, 1),
         .after = wto_d) %>%
  mutate(gatt_wto_both = if_else((gatt_wto_o == 1 & gatt_wto_d == 1), 1, 0))
```

## ASEAN specific modifications

```{r}
#create tech columns for 10 ASEAN member states by origin and destination
#and manually assign dummy 1 for ASEAN+1 agreement with Japan since 2008 (both general and directional for heterogeneity)
data_asean_selected <- data_asean_selected %>%
  mutate(asean_ms_o = case_when(iso3_o %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         asean_ms_d = case_when(iso3_d %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         rta_asean_plus = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN") | (year>=2008 & iso3_o=="JPN" & asean_ms_d==1) ~ 1, TRUE ~ 0),
         rta_asean_plus_a_j = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN" ~ 1), TRUE ~ 0),
         rta_asean_plus_j_a = case_when((year>=2008 & iso3_o=="JPN" & asean_ms_d==1 ~ 1), TRUE ~ 0))
```

# 1. Traditional Gravity Estimates

## Create necessary data

```{r}
# Select necessary years with 3 year intervals
asean_selected_tradit <- data_asean_selected %>%
  filter(year %in% seq(1965, 2020, 3))
```

```{r}
# Construct symmetric pair id's for exporter and importer
asean_selected_tradit <- asean_selected_tradit %>%
  mutate(pair = paste(pmin(iso3_o,iso3_d),pmax(iso3_o,iso3_d),sep = "_")) %>%
  group_by(pair) %>%
  mutate(pair_id = cur_group_id())
```

```{r}
# Construct exporter output and importer expenditure
#(is it GDPs?? Do we need to calculate them or can use gdp_o and gdp_d?)
# asean_selected_tradit <- asean_selected_tradit %>%
#   group_by(iso3_o,year) %>%
#   mutate(Y_it = sum(tradeflow_comtrade_d)) %>%
#   group_by(iso3_d,year) %>%
#   mutate(E_jt = sum(tradeflow_comtrade_d))
```

We have problems with zeroes here, we get -inf in logged columns. But should be fine if we specify in estimation that tradeflows\>0 for traditional estimates

```{r}
# calculate logs
# asean_selected_tradit <- asean_selected_tradit %>%
#   mutate(across(c(tradeflow_comtrade_d, Y_it, E_jt, dist, gdp_o, gdp_d), ~log(.x), .names="ln_{.col}"))
```

```{r}
# calculate logs
asean_selected_tradit <- asean_selected_tradit %>%
  mutate(across(c(tradeflow_comtrade_d, dist, gdp_o, gdp_d), ~log(.x), .names="ln_{.col}"))
```

## 1.1 Naive gravity estimation

```{r}
# Estimation with feols, which allows for FE and clusters

# without controlling for WTO, GATT and RTAs and with true gdp_o and gdp_d
fit_ols2 <- feols(ln_tradeflow_comtrade_d ~ ln_dist + ln_gdp_o + ln_gdp_d + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig,
                data = asean_selected_tradit %>%
                  filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d), 
                vcov = cluster ~ pair_id)
summary(fit_ols2) 
```

## 1.2. Proxy for MRT

```{r}
## Calculate remoteness indices - Should we use true GDP or proxies for remoteness indices?
asean_selected_tradit = asean_selected_tradit %>%
  filter(gdp_o > 0 & gdp_d > 0) %>%
  group_by(year) %>%
  mutate(Y_t = sum(gdp_o), E_t = sum(gdp_d)) %>%
  group_by(iso3_o, year) %>%
  mutate(remoteness_exp = sum(dist /(gdp_d / E_t))) %>%
  group_by(iso3_d, year) %>%
  mutate(remoteness_imp = sum(dist / (gdp_o / Y_t))) %>%
  mutate(ln_remoteness_exp = log(remoteness_exp), 
         ln_remoteness_imp = log(remoteness_imp))


##Estimation
fit_remoteness = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + ln_gdp_o + ln_gdp_d + ln_remoteness_exp + ln_remoteness_imp,
                       data = asean_selected_tradit %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                       vcov = cluster ~ pair_id)
summary(fit_remoteness) 
```

## 1.3. Fixed Effects

```{r}
## Create fixed effects 
asean_selected_tradit = asean_selected_tradit %>%
     unite("fe_exp_year",c(iso3_o,year),sep="_",remove=FALSE) %>%
     unite("fe_imp_year",c(iso3_d,year),sep="_",remove=FALSE) %>%
     relocate(c(fe_exp_year,fe_imp_year), .after = 5)#in order to make it clear in the table

## Estimation 
fit_fixedeffects = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both |
                           fe_exp_year + fe_imp_year,
                         data = asean_selected_tradit %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                         vcov = cluster ~ pair_id)
summary(fit_fixedeffects) 
# Why do we get this negative coefficient for comleg_posttrans? Especially because the one for comleg_pretrans is positive..
```

## 1.4. PPML with FE

```{r}
## PPML model
fit_poisson = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both |
                           fe_exp_year + fe_imp_year,
                     data = asean_selected_tradit %>% filter(iso3_o != iso3_d),
                     vcov = cluster ~ pair_id)
summary(fit_poisson)
```

## Overview
```{r}
table_tradit <- huxreg("  " = fit_ols2,
                       "with MRT" = fit_remoteness,
                       "with FE" = fit_fixedeffects,
                       " " = fit_poisson,
                       coefs = c("Intercept" = "(Intercept)",
                                 "Log exporter GDP" = "ln_gdp_o",
                                 "Log importer GDP" = "ln_gdp_d",
                                 "Log distance" = "ln_dist",
                                 "Language" = "comlang_off",
                                 "Colonizer" = "comcol",
                                 "Colonial relation" = "col45",
                                 "Legal origins before 1991" = "comleg_pretrans",
                                 "Legal origins after 1991" = "comleg_posttrans",
                                 "Religion" = "comrelig",
                                 "GATT/WTO" = "gatt_wto_both",
                                 "Exporter remoteness" = "ln_remoteness_exp",
                                 "Importer remoteness" = "ln_remoteness_imp"),
                       number_format = 3,
                       statistics = c("N"="nobs", "R^2"="r.squared", "pseudo R^2"="pseudo.r.squared"),
                       note = "Notes: Statistics based on author's calculations. All estimates are obtained with data for the period from 1965 to 2020 with 3-year intervals. Standard errors are clustered by country pair and are reported in parentheses. {stars}") %>%
  insert_row("", "(1) OLS", "(2) OLS", "(3) OLS", "(4) PPML", after = 0) %>%
  insert_row(c("Fixed Effects", "No", "No", "Yes", "Yes"), after = 29) %>%
  set_col_width(c(0.3,rep(0.9/4,4))) %>%
  set_align(everywhere,-1,"center") %>%
  set_top_border(1,everywhere,1) %>%
  set_bottom_border(29,everywhere,0) %>%
  set_tb_padding(0) %>%
  set_caption("Traditional Gravity Estimates") %>%
  set_label("table_tradit")
table_tradit
```
```{r}
width(table_tradit) = 1 #Set relative table width for use in documents
## Export table to word
table_tradit_docx = as_flextable(table_tradit)
save_as_docx(table_tradit_docx, path = "table_tradit.docx")
```



# 2. Estimates of RTAs (general RTA, not ASEAN specific)

## Create necessary data

```{r}
# Select necessary years with 3 year intervals
asean_selected_rta <- data_asean_selected %>%
  filter(year %in% seq(1965, 2020, 3))
```

```{r}
# Construct symmetric pair id's for exporter and importer
asean_selected_rta <- asean_selected_rta %>%
  mutate(pair = paste(pmin(iso3_o,iso3_d),pmax(iso3_o,iso3_d),sep = "_")) %>%
  group_by(pair) %>%
  mutate(pair_id = cur_group_id())
```

```{r}
# calculate logs
asean_selected_rta <- asean_selected_rta %>%
  mutate(across(c(tradeflow_comtrade_d, dist), ~log(.x), .names="ln_{.col}"))
```

```{r}
## Create fixed effects 
asean_selected_rta = asean_selected_rta %>%
     unite("fe_exp_year",c(iso3_o,year),sep="_",remove=FALSE) %>%
     unite("fe_imp_year",c(iso3_d,year),sep="_",remove=FALSE) %>%
     relocate(c(fe_exp_year,fe_imp_year), .after = 5)#in order to make it clear in the table
```

```{r}
## Specify country-specific intra-national trade dummies
asean_selected_rta = asean_selected_rta %>%
mutate(D_trade_ii = ifelse(iso3_o==iso3_d,iso3_o,"international"))
```

## 2.1. Traditional estimates of RTAs (OLS)

```{r}
## OLS estimation
rta_ols = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + rta + gatt_wto_both |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(ln_tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_ols)
```



## 2.2. Traditional estimates of RTAs (PPML)
```{r}
rta_poisson = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + rta + gatt_wto_both |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_poisson)
```

### we can also estimate regression where we split RTA in types after we select the preffered specification
```{r}
#see amount of observations by type of RTA
table(asean_selected_rta$rta_type)

rta_poisson_types = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + as.factor(rta_type) + gatt_wto_both |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_poisson_types)

# is it ok that some RTAs have negative effects? --- maybe we need to exclude combined types of RTA?
#type 3 (EIA) might be negative due to only 56 observations in the whole dataset, so it's not significant
#type 7 (PSA&EIA) might be negative due to less deep integration in Partial Scope Agreements (and it's also only 471 observations in total)
```



## 2.3. Allowing for trade diversion from domestic sales (includes FE for intra-trade)
```{r}
## PPML estimation
rta_poisson_intra = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + rta + gatt_wto_both |
                           fe_exp_year + fe_imp_year + D_trade_ii,
data = asean_selected_rta,
vcov = cluster ~ pair_id)

summary(rta_poisson_intra)
```



## 2.4. Addressing potential endogeneity of RTAs
```{r}
## PPML estimation
rta_endo = fepois(tradeflow_comtrade_d ~ rta + gatt_wto_both |
fe_exp_year + fe_imp_year + pair_id,
data = asean_selected_rta,
vcov = cluster ~ pair_id)

## Head of results
head(asean_selected_rta[-rta_endo$obs_selection$obsRemoved,
                        c("iso3_o","iso3_d","year","tradeflow_comtrade_d")] %>%
       arrange(iso3_o,iso3_d,year),3)

summary(rta_endo)
#rta coeff should be significant, why it's NOT???
```

## Overview
```{r}
table_rta <- huxreg("RTA" = rta_ols,
                    "RTA " = rta_poisson,
                    "RTA types" = rta_poisson_types,
                    "Intra-trade" = rta_poisson_intra,
                    "Endogeneity" = rta_endo,
                    coefs = c("Log distance" = "ln_dist",
                              "Language" = "comlang_off",
                              "Colonizer" = "comcol",
                              "Colonial relation" = "col45",
                              "Legal origins before 1991" = "comleg_pretrans",
                              "Legal origins after 1991" = "comleg_posttrans",
                              "Religion" = "comrelig",
                              "RTA" = "rta",
                              "GATT/WTO" = "gatt_wto_both",
                              "CU" = "as.factor(rta_type)1",
                              "CU & EIA" = "as.factor(rta_type)2",
                              "EIA" = "as.factor(rta_type)3",
                              "FTA" = "as.factor(rta_type)4",
                              "FTA & EIA" = "as.factor(rta_type)5",
                              "PSA & EIA" = "as.factor(rta_type)7"),
                    number_format = 3,
                    statistics = c("N"="nobs", "R^2"="r.squared", "pseudo R^2"="pseudo.r.squared"),
                    note = "Notes: Statistics based on author's calculations. All estimates are obtained with data for the period from 1965 to 2020 with 3-year intervals. Standard errors are clustered by country pair and are reported in parentheses. {stars}") %>%
  insert_row("","(1) OLS", "(2.1) PPML", "(2.2) PPML", "(3) PPML", "(4) PPML", after = 0) %>%
  insert_row(c("Intra-national trade", "No", "No", "No", "Yes", "Yes"), after = 33) %>%
  set_col_width(c(0.3,rep(0.9/5,5))) %>%
  set_align(everywhere,-1,"center") %>%
  set_top_border(1,everywhere,1) %>%
  set_tb_borders(34,everywhere,0) %>%
  set_tb_padding(0) %>%
  set_caption("Estimating General Effects of All Regional Trade Agreements") %>%
  set_label("table_rta")
table_rta
```

```{r}
width(table_rta) = 1 #Set relative table width for use in documents
## Export table to word
table_rta_docx = as_flextable(table_rta)
save_as_docx(table_rta_docx, path = "table_rta.docx")
```

# 3. Estimates of RTAs (ASEAN specific)

## Create necessary data

```{r}
#---create different columns for separating ASEAN dummy from general rta and rta_type -- needs to be set to 0 if manually created ASEAN dummy for Japan=1:

#adjust variables rta and rta_type by setting them to 0 if rta_asean_plus=1, so we don't duplicate when use both all RTA for RoW and specific Japan-ASEAN RTA in the regression
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta)),#general counterfactual
         rta_type_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta_type))) #specific counterfactual

#based on adjusted rta_type segregate agreements of Japan in different types of RTA if Japan is in origin or destination
asean_selected_rta <- asean_selected_rta %>%
  mutate(jpn_cu = if_else((rta_type_excl_asean_plus==1 & iso3_o=="JPN") | (rta_type_excl_asean_plus==1 & iso3_d=="JPN"), 1, 0),
         jpn_cu_eia = if_else((rta_type_excl_asean_plus==2 & iso3_o=="JPN") | (rta_type_excl_asean_plus==2 & iso3_d=="JPN"), 1, 0),
         jpn_eia = if_else((rta_type_excl_asean_plus==3 & iso3_o=="JPN") | (rta_type_excl_asean_plus==3 & iso3_d=="JPN"), 1, 0),
         jpn_fta = if_else((rta_type_excl_asean_plus==4 & iso3_o=="JPN") | (rta_type_excl_asean_plus==4 & iso3_d=="JPN"), 1, 0),
         jpn_fta_eia = if_else((rta_type_excl_asean_plus==5 & iso3_o=="JPN") | (rta_type_excl_asean_plus==5 & iso3_d=="JPN"), 1, 0),
         jpn_psa_eia = if_else((rta_type_excl_asean_plus==7 & iso3_o=="JPN") | (rta_type_excl_asean_plus==7 & iso3_d=="JPN"), 1, 0))


#again adjust rta_type by setting them to 0 if member of ANY type of agreement is Japan,
#if not, then keep adjusted rta_type from the 1st step. This way we will not duplicate them in the regression when use variables specifically for Japan and for RoW (namely, when we use in regression Japan-ASEAN, Japan in all types of RTAs with RoW, and all types of RTAs between other countries in RoW)
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_type_all_clean = if_else((jpn_cu==1) | (jpn_cu_eia==1) | (jpn_eia==1) | (jpn_fta==1) | (jpn_fta_eia==1) | (jpn_psa_eia==1), 0, as.numeric(rta_type_excl_asean_plus)))
```


## 3.1. Traditional estimates of RTAs (OLS)

```{r}
## OLS estimation
rta_ols_asean = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(ln_tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_ols_asean)
```

## 3.2. Traditional estimates of RTAs (PPML)
```{r}
rta_poisson_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_poisson_asean)
```
### we can also estimate regression where we split RTA in types after we select the preffered specification
```{r}
#see amount of observations by type of RTA
table(asean_selected_rta$rta_type)

rta_poisson_types_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + as.factor(rta_type_excl_asean_plus) + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_poisson_types_asean)

#type 3 (EIA) might be negative due to only 56 observations in the whole dataset, so it's not significant
#type 7 (PSA&EIA) might be negative due to less deep integration in Partial Scope Agreements (and it's also only 471 observations in total)
```

### adding variables for all 7 types of RTAs Japan is part of
```{r}
rta_poisson_jpntypes_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                           fe_exp_year + fe_imp_year,
data = asean_selected_rta %>%
filter(iso3_o != iso3_d),
vcov = cluster ~ pair_id)

summary(rta_poisson_jpntypes_asean)
```


## 3.3. Allowing for trade diversion from domestic sales (includes FE for intra-trade)
```{r}
## PPML estimation
rta_poisson_intra_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year + D_trade_ii,
data = asean_selected_rta,
vcov = cluster ~ pair_id)

summary(rta_poisson_intra_asean)
```

### adding variables for all 7 types of RTAs Japan is part of
```{r}
rta_poisson_jpntypes_intra_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                           fe_exp_year + fe_imp_year + D_trade_ii,
data = asean_selected_rta,
vcov = cluster ~ pair_id)

summary(rta_poisson_jpntypes_intra_asean)
```


## 3.4. Addressing potential endogeneity of RTAs
```{r}
## PPML estimation
rta_endo_asean = fepois(tradeflow_comtrade_d ~ gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
fe_exp_year + fe_imp_year + pair_id,
data = asean_selected_rta,
vcov = cluster ~ pair_id)

summary(rta_endo_asean)
#rta coeff should be significant, why it's NOT???
```

### adding variables for all 7 types of RTAs Japan is part of
```{r}
rta_jpntypes_endo_asean = fepois(tradeflow_comtrade_d ~ gatt_wto_both + rta_asean_plus + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
fe_exp_year + fe_imp_year + pair_id,
data = asean_selected_rta,
vcov = cluster ~ pair_id)

summary(rta_jpntypes_endo_asean)
#rta coeff should be significant, why it's NOT???
```

## Overview
```{r}
table_rta_asean <- huxreg("RTA" = rta_ols_asean,
                    "RTA " = rta_poisson_asean,
                    "RTA, types" = rta_poisson_jpntypes_asean,
                    "INTRA" = rta_poisson_intra_asean,
                    "INTRA, types" = rta_poisson_jpntypes_intra_asean,
                    "ENDG" = rta_endo_asean,
                    "ENDG, types" = rta_jpntypes_endo_asean,
                    coefs = c("Log distance" = "ln_dist",
                              "Language" = "comlang_off",
                              "Colonizer" = "comcol",
                              "Colonial relation" = "col45",
                              "Legal origins before 1991" = "comleg_pretrans",
                              "Legal origins after 1991" = "comleg_posttrans",
                              "Religion" = "comrelig",
                              "GATT/WTO" = "gatt_wto_both",
                              "RTA ASEAN-Japan" = "rta_asean_plus",
                              "RTA in RoW" = "rta_excl_asean_plus",
                              "Japan in FTA & EIA" = "jpn_fta_eia",
                              "CU in RoW" = "as.factor(rta_type_all_clean)1",
                              "CU & EIA in RoW" = "as.factor(rta_type_all_clean)2",
                              "EIA in RoW" = "as.factor(rta_type_all_clean)3",
                              "FTA in RoW" = "as.factor(rta_type_all_clean)4",
                              "FTA & EIA in RoW" = "as.factor(rta_type_all_clean)5",
                              "PSA & EIA in RoW" = "as.factor(rta_type_all_clean)7"),
                    number_format = 3,
                    statistics = c("N"="nobs", "R^2"="r.squared", "pseudo R^2"="pseudo.r.squared"),
                    note = "Notes: Statistics based on author's calculations. All estimates are obtained with data for the period from 1965 to 2020 with 3-year intervals. Standard errors are clustered by country pair and are reported in parentheses. {stars}") %>%
  insert_row("","(1) OLS", "(2.1) PPML", "(2.2) PPML", "(3) PPML", "(3.1) PPML", "(4) PPML", "(4.1) PPML", after = 0) %>%
  insert_row(c("Intra-national trade", "No", "No", "No", "Yes", "Yes", "Yes", "Yes"), after = 37) %>%
  insert_row(c("Japan in other RTAs", "No", "No", "Yes", "No", "Yes", "No", "Yes"), after = 38) %>%
  set_col_width(c(0.3,rep(0.9/7,7))) %>%
  set_align(everywhere,-1,"center") %>%
  set_top_border(1,everywhere,1) %>%
  set_tb_borders(33,everywhere,0) %>%
  set_tb_padding(0) %>%
  set_caption("Estimating General Effects of Japan's ASEAN+1 Agreement Compared to All Regional Trade Agreements") %>%
  set_label("table_rta_asean")
table_rta_asean
```

```{r}
width(table_rta_asean) = 1 #Set relative table width for use in documents
## Export table to word
table_rta_asean_docx = as_flextable(table_rta_asean)
save_as_docx(table_rta_asean_docx, path = "table_rta_asean.docx")
```



#-----------------------

# 4. All steps - Estimates of RTAs (ASEAN specific)

## 4.1.Naive gravity

### Data
```{r}
# Select necessary years with 3 year intervals
asean_selected_rta <- data_asean_selected %>%
  filter(year %in% seq(1965, 2020, 3))
```

```{r}
# Construct symmetric pair id's for exporter and importer
asean_selected_rta <- asean_selected_rta %>%
  mutate(pair = paste(pmin(iso3_o,iso3_d),pmax(iso3_o,iso3_d),sep = "_")) %>%
  group_by(pair) %>%
  mutate(pair_id = cur_group_id())
```

```{r}
# calculate logs
asean_selected_rta <- asean_selected_rta %>%
  mutate(across(c(tradeflow_comtrade_d, dist, gdp_o, gdp_d), ~log(.x), .names="ln_{.col}"))
```

```{r}
#---create different columns for separating ASEAN dummy from general rta and rta_type -- needs to be set to 0 if manually created ASEAN dummy for Japan=1:

#adjust variables rta and rta_type by setting them to 0 if rta_asean_plus=1, so we don't duplicate when use both all RTA for RoW and specific Japan-ASEAN RTA in the regression
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta)),#general counterfactual
         rta_type_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta_type))) #specific counterfactual

#based on adjusted rta_type segregate agreements of Japan in different types of RTA if Japan is in origin or destination
asean_selected_rta <- asean_selected_rta %>%
  mutate(jpn_cu = if_else((rta_type_excl_asean_plus==1 & iso3_o=="JPN") | (rta_type_excl_asean_plus==1 & iso3_d=="JPN"), 1, 0),
         jpn_cu_eia = if_else((rta_type_excl_asean_plus==2 & iso3_o=="JPN") | (rta_type_excl_asean_plus==2 & iso3_d=="JPN"), 1, 0),
         jpn_eia = if_else((rta_type_excl_asean_plus==3 & iso3_o=="JPN") | (rta_type_excl_asean_plus==3 & iso3_d=="JPN"), 1, 0),
         jpn_fta = if_else((rta_type_excl_asean_plus==4 & iso3_o=="JPN") | (rta_type_excl_asean_plus==4 & iso3_d=="JPN"), 1, 0),
         jpn_fta_eia = if_else((rta_type_excl_asean_plus==5 & iso3_o=="JPN") | (rta_type_excl_asean_plus==5 & iso3_d=="JPN"), 1, 0),
         jpn_psa_eia = if_else((rta_type_excl_asean_plus==7 & iso3_o=="JPN") | (rta_type_excl_asean_plus==7 & iso3_d=="JPN"), 1, 0))


#again adjust rta_type by setting them to 0 if member of ANY type of agreement is Japan,
#if not, then keep adjusted rta_type from the 1st step. This way we will not duplicate them in the regression when use variables specifically for Japan and for RoW (namely, when we use in regression Japan-ASEAN, Japan in all types of RTAs with RoW, and all types of RTAs between other countries in RoW)
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_type_all_clean = if_else((jpn_cu==1) | (jpn_cu_eia==1) | (jpn_eia==1) | (jpn_fta==1) | (jpn_fta_eia==1) | (jpn_psa_eia==1), 0, as.numeric(rta_type_excl_asean_plus)))
```


### OLS Estimation
```{r}
# Estimation with feols, which allows for FE and clusters

rta_fit_ols <- feols(ln_tradeflow_comtrade_d ~ ln_dist + ln_gdp_o + ln_gdp_d + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus,
                data = asean_selected_rta %>%
                  filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d), 
                vcov = cluster ~ pair_id)
summary(rta_fit_ols) 
```


## 4.2. Proxy for MRT

### Data
```{r}
asean_selected_rta = asean_selected_rta %>%
  filter(gdp_o > 0 & gdp_d > 0) %>%
  group_by(year) %>%
  mutate(Y_t = sum(gdp_o), E_t = sum(gdp_d)) %>%
  group_by(iso3_o, year) %>%
  mutate(remoteness_exp = sum(dist /(gdp_d / E_t))) %>%
  group_by(iso3_d, year) %>%
  mutate(remoteness_imp = sum(dist / (gdp_o / Y_t))) %>%
  mutate(ln_remoteness_exp = log(remoteness_exp), 
         ln_remoteness_imp = log(remoteness_imp))
```

### OLS Estimation
```{r}
rta_fit_remoteness = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + ln_gdp_o + ln_gdp_d + ln_remoteness_exp + ln_remoteness_imp + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus,
                       data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                       vcov = cluster ~ pair_id)
summary(rta_fit_remoteness) 
```


## 4.3. Fixed Effects - Traditional estimates of RTAs

### Data
```{r}
## Create fixed effects 
asean_selected_rta = asean_selected_rta %>%
     unite("fe_exp_year",c(iso3_o,year),sep="_",remove=FALSE) %>%
     unite("fe_imp_year",c(iso3_d,year),sep="_",remove=FALSE) %>%
     relocate(c(fe_exp_year,fe_imp_year), .after = 5)#in order to make it clear in the table
```

### OLS Estimation
```{r}
rta_fit_fixedeffects = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
                         data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                         vcov = cluster ~ pair_id)
summary(rta_fit_fixedeffects) 
```


## 4.4. Traditional estimates of RTAs

### PPML Estimation
```{r}
rta_poisson = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
                           data = asean_selected_rta %>% filter(iso3_o != iso3_d),
                           vcov = cluster ~ pair_id)

summary(rta_poisson)
```


## 4.5. Allowing for trade diversion from domestic sales (includes FE for intra-trade)

### Data
```{r}
## Specify country-specific intra-national trade dummies
asean_selected_rta = asean_selected_rta %>%
mutate(D_trade_ii = ifelse(iso3_o==iso3_d,iso3_o,"international"))
```

### PPML Estimation
```{r}
rta_poisson_intra = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra)
```
### Heterogeneity - PPML Estimation
```{r}
#with directions: Japan to ASEAN, ASEAN to Japan
rta_poisson_intra_dir = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus_a_j + rta_asean_plus_j_a |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra_dir)
```


```{r}
#with Japan in other RTAs
rta_poisson_intra_jpntypes = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra_jpntypes)
```

```{r}
#with everything
rta_poisson_intra_all = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus_a_j + rta_asean_plus_j_a + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra_all)
```

```{r}
fig_rta_types <- modelplot(rta_poisson_intra_all, coef_map = c("rta_asean_plus_a_j" = "RTA ASEAN --> Japan",
                                              "rta_asean_plus_j_a" = "RTA Japan --> ASEAN",
                                              "jpn_fta_eia" = "Japan in FTA & EIA",
                                              "as.factor(rta_type_all_clean)1" = "CU in RoW",
                                              "as.factor(rta_type_all_clean)2" = "CU & EIA in RoW",
                                              "as.factor(rta_type_all_clean)3" = "EIA in RoW",
                                              "as.factor(rta_type_all_clean)4" = "FTA in RoW",
                                              "as.factor(rta_type_all_clean)5" = "FTA & EIA in RoW",
                                              "as.factor(rta_type_all_clean)7" = "PSA & EIA in RoW")) +
  labs(x = "Gravity estimates", y = "Types of RTAs", title = "RTA Estimates by Type of Agreement") +
   aes(color = if_else(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("grey", "black")) +
  geom_vline(xintercept = 0, color = 'orange')

#caption = "All coefficients are estimated with PPML including intra-trade as in specification (4) after replacing the vector of RTA with different RTA types and specifying direction of exports for ASEAN+1 RTA"
```


## 4.6. Addressing potential endogeneity of RTAs 

### PPML Estimation
```{r}
rta_poisson_endo = fepois(tradeflow_comtrade_d ~ gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                          fe_exp_year + fe_imp_year + pair_id,
                        data = asean_selected_rta,
                        vcov = cluster ~ pair_id)

summary(rta_poisson_endo)
#rta coeff should be significant, why it's NOT???
```

### OLS Estimation
```{r}
rta_ols_endo = feols(ln_tradeflow_comtrade_d ~ gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                          fe_exp_year + fe_imp_year + pair_id,
                        data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                        vcov = cluster ~ pair_id)

summary(rta_ols_endo)
#RTA for ASEAN not signifficant, only significant for RoW
```


## Overview
```{r}
table_asean_steps <- huxreg("Naive" = rta_fit_ols,
                    "MRT" = rta_fit_remoteness,
                    "FE" = rta_fit_fixedeffects,
                    "INTRA" = rta_poisson_intra,
                    "ENDG" = rta_poisson_endo,
                    "ENDG " = rta_ols_endo,
                    coefs = c("Intercept" = "(Intercept)",
                              "Log exporter GDP" = "ln_gdp_o",
                              "Log importer GDP" = "ln_gdp_d",
                              "Exporter remoteness" = "ln_remoteness_exp",
                              "Importer remoteness" = "ln_remoteness_imp",
                              "Log distance" = "ln_dist",
                              "Language" = "comlang_off",
                              "Colonizer" = "comcol",
                              "Colonial relation" = "col45",
                              "Legal origins before 1991" = "comleg_pretrans",
                              "Legal origins after 1991" = "comleg_posttrans",
                              "Religion" = "comrelig",
                              "GATT/WTO" = "gatt_wto_both",
                              "RTA ASEAN-Japan" = "rta_asean_plus",
                              "RTA in RoW" = "rta_excl_asean_plus"),
                              #"Japan in FTA & EIA" = "jpn_fta_eia",
                              #"CU in RoW" = "as.factor(rta_type_all_clean)1",
                              #"CU & EIA in RoW" = "as.factor(rta_type_all_clean)2",
                              #"EIA in RoW" = "as.factor(rta_type_all_clean)3",
                              #"FTA in RoW" = "as.factor(rta_type_all_clean)4",
                              #"FTA & EIA in RoW" = "as.factor(rta_type_all_clean)5",
                              #"PSA & EIA in RoW" = "as.factor(rta_type_all_clean)7"),
                    number_format = 3,
                    statistics = c("N"="nobs", "R^2"="r.squared", "pseudo R^2"="pseudo.r.squared"),
                    note = "Notes: Statistics based on author's calculations. All estimates are obtained with data for the period from 1965 to 2020 with 3-year intervals. Standard errors are clustered by country pair and are reported in parentheses. {stars}") %>%
  insert_row("","(1) OLS", "(2) OLS", "(3) OLS", "(4) PPML", "(5) PPML", "(6) OLS", after = 0) %>%
  insert_row(c("Fixed Effects", "No", "No", "Yes", "Yes", "Yes", "Yes"), after = 33) %>%
  insert_row(c("Intra-national trade", "No", "No", "No", "Yes", "No", "No"), after = 34) %>%
  #insert_row(c("Japan in other RTAs", "No", "No", "Yes", "No", "Yes", "No", "Yes"), after = 38) %>%
  set_col_width(c(0.3,rep(0.9/6,6))) %>%
  set_align(everywhere,-1,"center") %>%
  set_top_border(1,everywhere,1) %>%
  set_bottom_border(31,everywhere,0) %>%
  set_tb_padding(0) %>%
  set_caption("Estimating General Effects of Japan's ASEAN+1 Agreement Compared to All Regional Trade Agreements") %>%
  set_label("table_asean_steps")
table_asean_steps
```






#--------------------
# 5. RTA Robustness Checks (ASEAN specific)

## 5.1. Testing for potential reverse causality between trade and RTAs
```{r}
## Identify future RTAs with custom function
asean_selected_rta = asean_selected_rta %>%
  group_by(iso3_o,iso3_d) %>%
  mutate(rta_excl_asean_plus_lead3 = tlead(rta_excl_asean_plus,n=3,along_with = year),
         rta_asean_plus_lead3 = tlead(rta_asean_plus, n=3, along_with = year))
```

```{r}
## Estimation
rta_lead_asean = feols(ln_tradeflow_comtrade_d ~  rta_excl_asean_plus + rta_excl_asean_plus_lead3 + rta_asean_plus + rta_asean_plus_lead3 |
                  fe_exp_year + fe_imp_year + pair_id,
                  data = asean_selected_rta, 
                  vcov = cluster ~ pair_id)

summary(rta_lead_asean)
#rta should be significant, but rta_lead3 NOT - this way we will correctly control for reverse causality

#is we estimate endogeneity with OLS, then it's ~okay here, cause RTA for RoW is signif, but RTA_lead3 not. But ASEAN RTA is problem...
```

## 5.2. Allowing for potential non-linear and phasing-in effects

```{r}
## Identify past RTAs to see how stronger effects get over time
asean_selected_rta = asean_selected_rta %>%
  group_by(iso3_o, iso3_d) %>%
  mutate(rta_excl_asean_plus_lag3 = tlag(rta_excl_asean_plus,n=3,along_with = year),
         rta_excl_asean_plus_lag6 = tlag(rta_excl_asean_plus,n=6,along_with = year),
         rta_excl_asean_plus_lag9 = tlag(rta_excl_asean_plus,n=9,along_with = year),
         rta_asean_plus_lag3 = tlag(rta_asean_plus,n=3,along_with = year),
         rta_asean_plus_lag6 = tlag(rta_asean_plus,n=6,along_with = year),
         rta_asean_plus_lag9 = tlag(rta_asean_plus,n=9,along_with = year))
```

```{r}
rta_lags_asean = feols(ln_tradeflow_comtrade_d ~  rta_asean_plus + rta_asean_plus_lag3 + rta_asean_plus_lag6 + rta_asean_plus_lag9 + rta_excl_asean_plus + rta_excl_asean_plus_lag3 + rta_excl_asean_plus_lag6 + rta_excl_asean_plus_lag9 |
                    fe_exp_year + fe_imp_year + pair_id,
                  data = asean_selected_rta, 
                  vcov = cluster ~ pair_id)

summary(rta_lags_asean)
#all coeffs of rta should be significant

#in our case even with OLS nothing from ASEAN is significant. And for RoW lags are signif, but original no...
```


## 5.3. Addressing globalization effects




# 6. RTA Robustness Checks (not ASEAN specific)

## 6.1. Testing for potential reverse causality between trade and RTAs
```{r}
## Identify future RTAs with custom function
asean_selected_rta = asean_selected_rta %>%
  group_by(iso3_o,iso3_d) %>%
  mutate(rta_lead3 = tlead(rta,n=3,along_with = year))
```

```{r}
## Estimation
rta_lead = fepois(tradeflow_comtrade_d ~  rta + rta_lead3 |
                    fe_exp_year + fe_imp_year + pair_id,
                  data = asean_selected_rta, 
                  vcov = cluster ~ pair_id)

summary(rta_lead)
#rta should be significant, but rta_lead3 NOT - this way we will correctly control for reverse causality
```


## 6.2. Allowing for potential non-linear and phasing-in effects

```{r}
## Identify past RTAs to see how stronger effects get over time
asean_selected_rta = asean_selected_rta %>%
  group_by(iso3_o, iso3_d) %>%
  mutate(rta_lag3 = tlag(rta,n=3,along_with = year),
         rta_lag6 = tlag(rta,n=6,along_with = year),
         rta_lag9 = tlag(rta,n=9,along_with = year))
```

```{r}
rta_lags = fepois(tradeflow_comtrade_d ~  rta + rta_lag3 + rta_lag6 + rta_lag9 |
                    fe_exp_year + fe_imp_year + pair_id,
                  data = asean_selected_rta, 
                  vcov = cluster ~ pair_id)

summary(rta_lags)
#all coeffs of rta should be significant
```


## 6.3. Addressing globalization effects











TRIALS (NOT MAIN CODE)

```{r}
class(data_asean_selected$rta_type)
table(data_asean_selected$rta)
```

```{r}
table(data_asean_selected$country_id_d, data_asean_selected$country_exists_d)
asean_selected_tradit %>% filter(wto_o == 1)
```

```{r}
sum(is.na(asean_selected_tradit$Y_it))
colSums(is.na(asean_selected_tradit))
```


 Descriptive statistics
Full Sample
```{r}
dim(data_asean_selected)[1] #number of observations
table(data_asean_selected$rta)[2] #number of observations for RTA

```

Sample with 3 year intervals
```{r}
dim(asean_selected_rta)[1] #number of observations
table(asean_selected_rta$rta)[2] #number of observations for RTA
```


