---
title: "RIA final project - Evolution of Japan’s trade flows after signing the ASEAN+1 agreement on Comprehensive Economic-Partnership in 2008."
author: "Kateryna Hanina, Gaelle Debree, Adele Verron"
toc: true
toc-location: body
format:
  html:
    code-fold: false
    self-contained: true
    page-layout: full
---

Countries (11): Brunei (BRN), Cambodia (KHM), Indonesia (IDN), Laos (LAO), Malaysia (MYS), Myanmar (MMR), Philippines (PHL), Singapore (SGP), Thailand (THA), Vietnam (VNM), Japan (JPN).

# General

```{r}
library(tidyverse)
library(fixest) # perform estimations with multiple fixed-effects
library(stargazer)
library(flextable)
library(huxtable)
library(modelsummary)
```

# Custom formulas

```{r}
# To get lagged values in function of CONSECUTIVE observations (here years)
tlag <- function(x, n = 1L, along_with, default = NA) { 
  if (!is.numeric(n) | (length(n)>1)) stop("n must be a numeric of length one")
  index <- match(along_with - n, along_with, incomparables = NA)
  out <- x[index]
  if (!is.na(default)) out[which(is.na(index))] <- default
  out
}
```

```{r}
# To get lead values in function of CONSECUTIVE observations (here years)
tlead <- function(x, n = 1L, along_with, default = NA) { 
  if (!is.numeric(n) | (length(n)>1)) stop("n must be a numeric of length one")
  index <- match(along_with + n, along_with, incomparables = NA)
  out <- x[index]
  if (!is.na(default)) out[which(is.na(index))] <- default
  out
}
```


# Data

```{r}
data_asean_raw <- read.csv("./Gravity_csv_V202211/Gravity_V202211.csv")
```

## General modifications

```{r}
#Select only countries and columns we need
#remove non-existing countries after they started existing in different form (+Singapore independence since 1965)
#remove tech variables
data_asean_selected <- data_asean_raw %>%
  select(c(year, country_id_o, country_id_d, iso3_o, iso3_d, country_exists_o, country_exists_d, dist, comlang_off, comlang_ethno, comcol, col45, comleg_pretrans, comleg_posttrans, comrelig, col_dep_end_conflict, gdp_o, gdp_d, gatt_o, gatt_d, wto_o, wto_d, rta_type, tradeflow_comtrade_d)) %>%
  filter(year >= 1965 & country_exists_o == 1 & country_exists_d == 1) %>%
  select(-c(country_id_o, country_id_d, country_exists_o, country_exists_d))
```

```{r}
#set rta_type and trade flows to 0 if NA
data_asean_selected <- data_asean_selected %>%
  mutate(rta_type = coalesce(rta_type, 0),
         tradeflow_comtrade_d = coalesce(tradeflow_comtrade_d, 0))
```

```{r}
#create new columns:
#general presence in either GATT or WTO by origin and destination
#general dummy for presence of any RTA for all countries
#dummy for presence in either GATT or WTO if both countries are members of it
data_asean_selected <- data_asean_selected %>%
  mutate(gatt_wto_o = case_when((gatt_o == 1 | wto_o == 1) ~ 1, TRUE ~ 0),
         gatt_wto_d = case_when((gatt_d == 1 | wto_d == 1) ~ 1, TRUE ~ 0),
         rta = if_else(rta_type == 0, 0, 1),
         .after = wto_d) %>%
  mutate(gatt_wto_both = if_else((gatt_wto_o == 1 & gatt_wto_d == 1), 1, 0))
```

## ASEAN specific modifications

```{r}
#create tech columns for 10 ASEAN member states by origin and destination
#and manually assign dummy 1 for ASEAN+1 agreement with Japan since 2008 (both general and directional for heterogeneity)
data_asean_selected <- data_asean_selected %>%
  mutate(asean_ms_o = case_when(iso3_o %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         asean_ms_d = case_when(iso3_d %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         rta_asean_plus = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN") | (year>=2008 & iso3_o=="JPN" & asean_ms_d==1) ~ 1, TRUE ~ 0),
         rta_asean_plus_a_j = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN" ~ 1), TRUE ~ 0),
         rta_asean_plus_j_a = case_when((year>=2008 & iso3_o=="JPN" & asean_ms_d==1 ~ 1), TRUE ~ 0))
```


#-----------------------

# All steps - Estimates of RTAs (ASEAN specific)

## 1.Naive gravity

### Data
```{r}
# Select necessary years with 3 year intervals
asean_selected_rta <- data_asean_selected %>%
  filter(year %in% seq(1965, 2020, 3))
```

```{r}
# Construct symmetric pair id's for exporter and importer
asean_selected_rta <- asean_selected_rta %>%
  mutate(pair = paste(pmin(iso3_o,iso3_d),pmax(iso3_o,iso3_d),sep = "_")) %>%
  group_by(pair) %>%
  mutate(pair_id = cur_group_id())
```

```{r}
# calculate logs
asean_selected_rta <- asean_selected_rta %>%
  mutate(across(c(tradeflow_comtrade_d, dist, gdp_o, gdp_d), ~log(.x), .names="ln_{.col}"))
```

```{r}
#---create different columns for separating ASEAN dummy from general rta and rta_type -- needs to be set to 0 if manually created ASEAN dummy for Japan=1:

#adjust variables rta and rta_type by setting them to 0 if rta_asean_plus=1, so we don't duplicate when use both all RTA for RoW and specific Japan-ASEAN RTA in the regression
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta)),#general counterfactual
         rta_type_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta_type))) #specific counterfactual

#based on adjusted rta_type segregate agreements of Japan in different types of RTA if Japan is in origin or destination
asean_selected_rta <- asean_selected_rta %>%
  mutate(jpn_cu = if_else((rta_type_excl_asean_plus==1 & iso3_o=="JPN") | (rta_type_excl_asean_plus==1 & iso3_d=="JPN"), 1, 0),
         jpn_cu_eia = if_else((rta_type_excl_asean_plus==2 & iso3_o=="JPN") | (rta_type_excl_asean_plus==2 & iso3_d=="JPN"), 1, 0),
         jpn_eia = if_else((rta_type_excl_asean_plus==3 & iso3_o=="JPN") | (rta_type_excl_asean_plus==3 & iso3_d=="JPN"), 1, 0),
         jpn_fta = if_else((rta_type_excl_asean_plus==4 & iso3_o=="JPN") | (rta_type_excl_asean_plus==4 & iso3_d=="JPN"), 1, 0),
         jpn_fta_eia = if_else((rta_type_excl_asean_plus==5 & iso3_o=="JPN") | (rta_type_excl_asean_plus==5 & iso3_d=="JPN"), 1, 0),
         jpn_psa_eia = if_else((rta_type_excl_asean_plus==7 & iso3_o=="JPN") | (rta_type_excl_asean_plus==7 & iso3_d=="JPN"), 1, 0))


#again adjust rta_type by setting them to 0 if member of ANY type of agreement is Japan,
#if not, then keep adjusted rta_type from the 1st step. This way we will not duplicate them in the regression when use variables specifically for Japan and for RoW (namely, when we use in regression Japan-ASEAN, Japan in all types of RTAs with RoW, and all types of RTAs between other countries in RoW)
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_type_all_clean = if_else((jpn_cu==1) | (jpn_cu_eia==1) | (jpn_eia==1) | (jpn_fta==1) | (jpn_fta_eia==1) | (jpn_psa_eia==1), 0, as.numeric(rta_type_excl_asean_plus)))
```


### OLS Estimation
```{r}
# Estimation with feols, which allows for FE and clusters

rta_fit_ols <- feols(ln_tradeflow_comtrade_d ~ ln_dist + ln_gdp_o + ln_gdp_d + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus,
                data = asean_selected_rta %>%
                  filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d), 
                vcov = cluster ~ pair_id)
summary(rta_fit_ols) 
```


## 2. Proxy for MRT

### Data
```{r}
asean_selected_rta = asean_selected_rta %>%
  filter(gdp_o > 0 & gdp_d > 0) %>%
  group_by(year) %>%
  mutate(Y_t = sum(gdp_o), E_t = sum(gdp_d)) %>%
  group_by(iso3_o, year) %>%
  mutate(remoteness_exp = sum(dist /(gdp_d / E_t))) %>%
  group_by(iso3_d, year) %>%
  mutate(remoteness_imp = sum(dist / (gdp_o / Y_t))) %>%
  mutate(ln_remoteness_exp = log(remoteness_exp), 
         ln_remoteness_imp = log(remoteness_imp))
```

### OLS Estimation
```{r}
rta_fit_remoteness = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + ln_gdp_o + ln_gdp_d + ln_remoteness_exp + ln_remoteness_imp + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus,
                       data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                       vcov = cluster ~ pair_id)
summary(rta_fit_remoteness) 
```


## 3. Fixed Effects - Traditional estimates of RTAs

### Data
```{r}
## Create fixed effects 
asean_selected_rta = asean_selected_rta %>%
     unite("fe_exp_year",c(iso3_o,year),sep="_",remove=FALSE) %>%
     unite("fe_imp_year",c(iso3_d,year),sep="_",remove=FALSE) %>%
     relocate(c(fe_exp_year,fe_imp_year), .after = 5)#in order to make it clear in the table
```

### OLS Estimation
```{r}
rta_fit_fixedeffects = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
                         data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                         vcov = cluster ~ pair_id)
summary(rta_fit_fixedeffects) 
```


## 4. Traditional estimates of RTAs

### PPML Estimation
```{r}
rta_poisson = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year,
                           data = asean_selected_rta %>% filter(iso3_o != iso3_d),
                           vcov = cluster ~ pair_id)

summary(rta_poisson)
```


## 5. Allowing for trade diversion from domestic sales (includes FE for intra-trade)

### Data
```{r}
## Specify country-specific intra-national trade dummies
asean_selected_rta = asean_selected_rta %>%
mutate(D_trade_ii = ifelse(iso3_o==iso3_d,iso3_o,"international"))
```

### PPML Estimation
```{r}
rta_poisson_intra = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra)
```
### Heterogeneity - PPML Estimation
```{r}
#with directions: Japan to ASEAN, ASEAN to Japan
rta_poisson_intra_dir = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus_a_j + rta_asean_plus_j_a |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra_dir)
```


```{r}
#with Japan in other RTAs
rta_poisson_intra_jpntypes = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra_jpntypes)
```

```{r}
#with everything
rta_poisson_intra_all = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus_a_j + rta_asean_plus_j_a + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_poisson_intra_all)
```

```{r}
fig_rta_types <- modelplot(rta_poisson_intra_all, coef_map = c("rta_asean_plus_a_j" = "RTA ASEAN --> Japan",
                                              "rta_asean_plus_j_a" = "RTA Japan --> ASEAN",
                                              "jpn_fta_eia" = "Japan in FTA & EIA",
                                              "as.factor(rta_type_all_clean)1" = "CU in RoW",
                                              "as.factor(rta_type_all_clean)2" = "CU & EIA in RoW",
                                              "as.factor(rta_type_all_clean)3" = "EIA in RoW",
                                              "as.factor(rta_type_all_clean)4" = "FTA in RoW",
                                              "as.factor(rta_type_all_clean)5" = "FTA & EIA in RoW",
                                              "as.factor(rta_type_all_clean)7" = "PSA & EIA in RoW")) +
  labs(x = "Gravity estimates", y = "Types of RTAs", title = "RTA Estimates by Type of Agreement") +
   aes(color = if_else(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("grey", "black")) +
  geom_vline(xintercept = 0, color = 'orange')

fig_rta_types

#caption = "All coefficients are estimated with PPML including intra-trade as in specification (4) after replacing the vector of RTA with different RTA types and specifying direction of exports for ASEAN+1 RTA"
```
## 6. Testing for potential reverse causality between trade and RTAs
```{r}
## Identify future RTAs with custom function
asean_selected_rta = asean_selected_rta %>%
  group_by(iso3_o,iso3_d) %>%
  mutate(rta_excl_asean_plus_lead3 = tlead(rta_excl_asean_plus,n=3,along_with = year),
         rta_asean_plus_lead3 = tlead(rta_asean_plus, n=3, along_with = year),
         rta_excl_asean_plus_lead6 = tlead(rta_excl_asean_plus,n=6,along_with = year),
         rta_asean_plus_lead6 = tlead(rta_asean_plus, n=6, along_with = year),
         rta_excl_asean_plus_lead9 = tlead(rta_excl_asean_plus,n=9,along_with = year),
         rta_asean_plus_lead9 = tlead(rta_asean_plus, n=9, along_with = year))
```

```{r}
#PPML with intra
rta_lead_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_excl_asean_plus + rta_asean_plus + rta_excl_asean_plus_lead3 +rta_asean_plus_lead3 |
                           fe_exp_year + fe_imp_year + D_trade_ii,
                           data = asean_selected_rta,
                           vcov = cluster ~ pair_id)

summary(rta_lead_asean)
```


## 7. Addressing potential endogeneity of RTAs (to correct for reverse causality)

### PPML Estimation
```{r}
rta_poisson_endo = fepois(tradeflow_comtrade_d ~ gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                          fe_exp_year + fe_imp_year + pair_id,
                        data = asean_selected_rta,
                        vcov = cluster ~ pair_id)

summary(rta_poisson_endo)
#all rta coeff insignificant, some problem in dataset --> try OLS
```

### OLS Estimation
```{r}
#for general RTAs
rta_ols_endo = feols(ln_tradeflow_comtrade_d ~ gatt_wto_both + rta_excl_asean_plus + rta_asean_plus |
                          fe_exp_year + fe_imp_year + pair_id,
                        data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                        vcov = cluster ~ pair_id)

summary(rta_ols_endo)
#RTA for ASEAN not signifficant, only significant for RoW



#for all types of RTAs
rta_ols_endo_det = feols(ln_tradeflow_comtrade_d ~ gatt_wto_both + rta_asean_plus_a_j + rta_asean_plus_j_a + jpn_cu + jpn_cu_eia + jpn_eia + jpn_fta + jpn_fta_eia + jpn_psa_eia + as.factor(rta_type_all_clean) |
                          fe_exp_year + fe_imp_year + pair_id,
                        data = asean_selected_rta %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                        vcov = cluster ~ pair_id)

summary(rta_ols_endo_det)

```


## Overview
```{r}
table_asean_steps <- huxreg("Naive" = rta_fit_ols,
                    "MRT" = rta_fit_remoteness,
                    "FE" = rta_fit_fixedeffects,
                    "INTRA" = rta_poisson_intra,
                    "RVRS" = rta_lead_asean,
                    "ENDG " = rta_ols_endo,
                    coefs = c("Intercept" = "(Intercept)",
                              "Log exporter GDP" = "ln_gdp_o",
                              "Log importer GDP" = "ln_gdp_d",
                              "Exporter remoteness" = "ln_remoteness_exp",
                              "Importer remoteness" = "ln_remoteness_imp",
                              "Log distance" = "ln_dist",
                              "Language" = "comlang_off",
                              "Colonizer" = "comcol",
                              "Colonial relation" = "col45",
                              "Legal origins before 1991" = "comleg_pretrans",
                              "Legal origins after 1991" = "comleg_posttrans",
                              "Religion" = "comrelig",
                              "GATT/WTO" = "gatt_wto_both",
                              "RTA in RoW" = "rta_excl_asean_plus",
                              "RTA ASEAN-Japan" = "rta_asean_plus",
                              "RTA in RoW(t+3)" = "rta_excl_asean_plus_lead3",
                              "RTA ASEAN-Japan(t+3)" = "rta_asean_plus_lead3"),
                    number_format = 3,
                    statistics = c("N"="nobs", "R^2"="r.squared", "pseudo R^2"="pseudo.r.squared"),
                    note = "Notes: Statistics based on author's calculations. All estimates are obtained with data for the period from 1965 to 2020 with 3-year intervals. Standard errors are clustered by country pair and are reported in parentheses. {stars}") %>%
  insert_row("","(1) OLS", "(2) OLS", "(3) OLS", "(4) PPML", "(5) PPML", "(6) OLS", after = 0) %>%
  insert_row(c("Fixed Effects", "No", "No", "Yes", "Yes", "Yes", "Yes"), after = 37) %>%
  insert_row(c("Intra-national trade", "No", "No", "No", "Yes", "Yes", "No"), after = 38) %>%
  #insert_row(c("Japan in other RTAs", "No", "No", "Yes", "No", "Yes", "No", "Yes"), after = 38) %>%
  set_col_width(c(0.3,rep(0.9/6,6))) %>%
  set_align(everywhere,-1,"center") %>%
  set_top_border(1,everywhere,1) %>%
  set_bottom_border(34,everywhere,0) %>%
  set_tb_padding(0) %>%
  set_caption("Estimating General Effects of Japan's ASEAN+1 Agreement Compared to All Regional Trade Agreements") %>%
  set_label("table_asean_steps")
table_asean_steps
```

```{r}
width(table_asean_steps) = 1 #Set relative table width for use in documents
## Export table to word
table_asean_steps_docx = as_flextable(table_asean_steps)
save_as_docx(table_asean_steps_docx, path = "table_asean_steps.docx")
```


```{r}
table_asean_detailed <- huxreg("Directional" = rta_poisson_intra_dir,
                               "RTA Types" = rta_poisson_intra_all,
                               "ENDG - RTA Types" = rta_ols_endo_det,
                    coefs = c("Log distance" = "ln_dist",
                              "Language" = "comlang_off",
                              "Colonizer" = "comcol",
                              "Colonial relation" = "col45",
                              "Legal origins before 1991" = "comleg_pretrans",
                              "Legal origins after 1991" = "comleg_posttrans",
                              "Religion" = "comrelig",
                              "GATT/WTO" = "gatt_wto_both",
                              "RTA in RoW" = "rta_excl_asean_plus",
                              "RTA ASEAN --> Japan" = "rta_asean_plus_a_j",
                              "RTA Japan --> ASEAN" = "rta_asean_plus_j_a",
                              "Japan in FTA & EIA" = "jpn_fta_eia",
                              "CU in RoW" = "as.factor(rta_type_all_clean)1",
                              "CU & EIA in RoW" = "as.factor(rta_type_all_clean)2",
                              "EIA in RoW" = "as.factor(rta_type_all_clean)3",
                              "FTA in RoW" = "as.factor(rta_type_all_clean)4",
                              "FTA & EIA in RoW" = "as.factor(rta_type_all_clean)5",
                              "PSA & EIA in RoW" = "as.factor(rta_type_all_clean)7"),
                    number_format = 3,
                    error_pos = "same",
                    statistics = c("N"="nobs","R^2"="r.squared", "pseudo R^2"="pseudo.r.squared"),
                    note = "Notes: Statistics based on author's calculations. All estimates are obtained with data for the period from 1965 to 2020 with 3-year intervals. Standard errors are clustered by country pair and are reported in parentheses. {stars}") %>%
  insert_row("","(1) PPML", "(2) PPML", "(3) OLS", after = 0) %>%
  insert_row(c("Fixed Effects", "Yes", "Yes", "Yes"), after = 21) %>%
  insert_row(c("Intra-national trade", "Yes", "Yes", "No"), after = 22) %>%
  #insert_row(c("Japan in other RTAs", "No", "No", "Yes", "No", "Yes", "No", "Yes"), after = 38) %>%
  set_col_width(c(0.3,rep(0.9/3,3))) %>%
  set_align(everywhere,-1,"center") %>%
  set_top_border(1,everywhere,1) %>%
  set_tb_borders(10,everywhere,0) %>%
  set_tb_padding(0) %>%
  set_caption("Estimating Heterogeneous Effects of Japan's ASEAN+1 Agreement") %>%
  set_label("table_asean_detailed")
table_asean_detailed
```

```{r}
width(table_asean_detailed) = 1 #Set relative table width for use in documents
## Export table to word
table_asean_detailed_docx = as_flextable(table_asean_detailed)
save_as_docx(table_asean_detailed_docx, path = "table_asean_detailed.docx")
```



#---------------------


```{r echo=FALSE}
#  RTA Robustness Checks (ASEAN specific)
## 2. Allowing for potential non-linear and phasing-in effects

## Identify past RTAs to see how stronger effects get over time
asean_selected_rta = asean_selected_rta %>%
  group_by(iso3_o, iso3_d) %>%
  mutate(rta_excl_asean_plus_lag3 = tlag(rta_excl_asean_plus,n=3,along_with = year),
         rta_excl_asean_plus_lag6 = tlag(rta_excl_asean_plus,n=6,along_with = year),
         rta_excl_asean_plus_lag9 = tlag(rta_excl_asean_plus,n=9,along_with = year),
         rta_asean_plus_lag3 = tlag(rta_asean_plus,n=3,along_with = year),
         rta_asean_plus_lag6 = tlag(rta_asean_plus,n=6,along_with = year),
         rta_asean_plus_lag9 = tlag(rta_asean_plus,n=9,along_with = year))
```

```{r echo=FALSE}
#for PPML with intra
#rta_lags_asean = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + gatt_wto_both + rta_asean_plus + rta_asean_plus_lag3 + rta_asean_plus_lag6 + rta_asean_plus_lag9 + rta_excl_asean_plus + rta_excl_asean_plus_lag3 + rta_excl_asean_plus_lag6 + rta_excl_asean_plus_lag9 |
                  #   fe_exp_year + fe_imp_year + D_trade_ii,
                  # data = asean_selected_rta, 
                  # vcov = cluster ~ pair_id)

#summary(rta_lags_asean)
# for RoW there is effect afterwards, for ASEAN no
```


