---
title: "RIA final project - Evolution of Japan's trade flows after signing the ASEAN+1 in 1977"
author: "Kateryna Hanina"
format: html
---

Countries (11): Brunei (BRN), Cambodia (KHM), Indonesia (IDN), Laos (LAO), Malaysia (MYS), Myanmar (MMR), Philippines (PHL), Singapore (SGP), Thailand (THA), Vietnam (VNM), Japan (JPN).


# General
```{r}
library(tidyverse)
library(fixest) # perform estimations with multiple fixed-effects
library(stargazer)
```


# Data

```{r}
data_asean_raw <- read.csv("./Gravity_csv_V202211/Gravity_V202211.csv")
```


## General modifications
```{r}
#Select only countries and columns we need
#remove non-existing countries after they started existing in different form (+Singapore independence since 1965)
#remove tech variables
data_asean_selected <- data_asean_raw %>%
  select(c(year, country_id_o, country_id_d, iso3_o, iso3_d, country_exists_o, country_exists_d, dist, comlang_off, comlang_ethno, comcol, col45, comleg_pretrans, comleg_posttrans, comrelig, col_dep_end_conflict, gdp_o, gdp_d, gatt_o, gatt_d, wto_o, wto_d, rta_type, tradeflow_comtrade_d)) %>%
  filter(year >= 1965 & country_exists_o == 1 & country_exists_d == 1) %>%
  select(-c(country_id_o, country_id_d, country_exists_o, country_exists_d))
```

```{r}
#set rta_type and trade flows to 0 if NA
data_asean_selected <- data_asean_selected %>%
  mutate(rta_type = coalesce(rta_type, 0),
         tradeflow_comtrade_d = coalesce(tradeflow_comtrade_d, 0))
```

```{r}
#create new column: general dummy for presence of any RTA for all countries
data_asean_selected <- data_asean_selected %>%
  mutate(rta = if_else(rta_type == 0, "0", "1"), .after = wto_d)
```

## ASEAN specific modifications
```{r}
#create tech columns for 10 ASEAN member states by origin and destination
#and manually assign dummy 1 for ASEAN+1 agreement with Japan since 2008
data_asean_selected <- data_asean_selected %>%
  mutate(asean_ms_o = case_when(iso3_o %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         asean_ms_d = case_when(iso3_d %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         rta_asean_plus = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN") | (year>=2008 & iso3_o=="JPN" & asean_ms_d==1) ~ 1, TRUE ~ 0))
```





# Traditional Graivity Estimates

## 1. Naive gravity
```{r}
# Select necessary years with 3 year intervals
asean_selected_tradit <- data_asean_selected %>%
  filter(year %in% seq(1965, 2020, 3))
```

```{r}
# Construct symmetric pair id's for exporter and importer
asean_selected_tradit <- asean_selected_tradit %>%
  mutate(pair = paste(pmin(iso3_o,iso3_d),pmax(iso3_o,iso3_d),sep = "_")) %>%
  group_by(pair) %>%
  mutate(pair_id = cur_group_id())


# Construct exporter output and importer expenditure
#(is it GDPs?? Do we need to calculate them or can use gdp_o and gdp_d?)
asean_selected_tradit <- asean_selected_tradit %>%
  group_by(iso3_o,year) %>%
  mutate(Y_it = sum(tradeflow_comtrade_d)) %>%
  group_by(iso3_d,year) %>%
  mutate(E_jt = sum(tradeflow_comtrade_d))
```


We have problems with zeroes here, we get -inf in logged columns. But should be fine if we specify in estimation that tradeflows>0 for traditional estimates
```{r}
# calculate logs
asean_selected_tradit <- asean_selected_tradit %>%
  mutate(across(c(tradeflow_comtrade_d, Y_it, E_jt, dist, gdp_o, gdp_d), ~log(.x), .names="ln_{.col}"))
```

```{r}
# Estimation with feols, which allows for FE and clusters

# without controlling for WTO, GATT and RTAs and with calculated Y and E
fit_ols1 <- feols(ln_tradeflow_comtrade_d ~ ln_dist + ln_Y_it + ln_E_jt + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig,
                data = asean_selected_tradit %>%
                  filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d), 
                vcov = cluster ~ pair_id)
summary(fit_ols1)

# without controlling for WTO, GATT and RTAs and with true gdp_o and gdp_d
fit_ols2 <- feols(ln_tradeflow_comtrade_d ~ ln_dist + ln_gdp_o + ln_gdp_d + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig,
                data = asean_selected_tradit %>%
                  filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d), 
                vcov = cluster ~ pair_id)
summary(fit_ols2) 
#ADELE: For me results are less significants with true gdp values
#GAELLE: Prof uses Y and E for the naive gravity model, note the true gdp + agree with Adèle
```


## 2. Proxy for MRT

```{r}
## Calculate remoteness indices
asean_selected_tradit = asean_selected_tradit %>%
  filter(Y_it > 0 & E_jt >0) %>%
  group_by(year) %>%
  mutate(Y_t = sum(Y_it), E_t = sum(E_jt)) %>%
  group_by(iso3_o, year) %>%
  mutate(remoteness_exp = sum(dist /(E_jt / E_t))) %>%
  group_by(iso3_d, year) %>%
  mutate(remoteness_imp = sum(dist / (Y_it / Y_t))) %>%
  mutate(ln_remoteness_exp = log(remoteness_exp), 
         ln_remoteness_imp = log(remoteness_imp))
#Adele: Weird results for the log of remoteness(??) -- Katya: I tried to add condition on Y and E >0 and then it estimated fine (but not sure we are allowed to deal with zeroes in Y and E in this way)

##Estimation
fit_remoteness = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + ln_Y_it + ln_E_jt + ln_remoteness_exp + ln_remoteness_imp,
                       data = asean_selected_tradit %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                       vcov = cluster ~ pair_id)
summary(fit_remoteness) # Adele:better R^2 (65%) with adding remoteness --- Katya: I removed variable for conflict, cause we loose too many observations, then with this estimation we have R^2 56%, almost the same as in naive model

#Adele:When I run it I got "All observations contain NAs. Estimation cannot be done. Check whether you know how to fix it. --- Katya: fixed with >0 for Y and E (not sure we can do it)

#Gaelle: sounds weird to deal with zeros but if it only works like this, then I think that it is correct
```

## 3. Fixed Effects
```{r}
## Create fixed effects 
asean_selected_tradit = asean_selected_tradit %>%
     unite("fe_exp_year",c(iso3_o,year),sep="_",remove=FALSE) %>%
     unite("fe_imp_year",c(iso3_d,year),sep="_",remove=FALSE) %>%
     relocate(c(fe_exp_year,fe_imp_year), .after = 5)#in order to make it clear in the table

## Estimation 
fit_fixedeffects = feols(ln_tradeflow_comtrade_d ~ ln_dist + comlang_off + comlang_ethno + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + col_dep_end_conflict + ln_Y_it + ln_E_jt |
                           fe_exp_year + fe_imp_year,
                         data = asean_selected_tradit %>% filter(tradeflow_comtrade_d > 0 & iso3_o != iso3_d),
                         vcov = cluster ~ pair_id)
summary(fit_fixedeffects) #probably something wrong in the variance here because R^2=1 (not impossible but low chances to get this result)

#Gaelle: in the slides, he removed ln_Y_it and ln_E_jt because he said that there was collinearity BUT, with removing it, we still find R2=1 which is weird. Moreover, it says that 5 variables have been removed because of collinearity. How to fix that?
```



## 4. PPML with FE
```{r}
## PPML model
fit_poisson = fepois(tradeflow_comtrade_d ~ ln_dist + comlang_off + comlang_ethno + comcol + col45 + comleg_pretrans + comleg_posttrans + comrelig + col_dep_end_conflict |
                           fe_exp_year + fe_imp_year,
                     data = asean_selected_tradit %>% filter(iso3_o != iso3_d),
                     vcov = cluster ~ pair_id)
summary(fit_poisson)

#A lot of observations were removed because of NAs and also 'comleg_posttrans' because of colinearity. Different results from OLS but adj. pseudo R2=0.99

## Robustness check of PPML
```







TRIALS (NOT MAIN CODE)
```{r}
class(data_asean_selected$rta_type)
table(data_asean_selected$rta)
```

```{r}
find_rta <- data_asean_selected %>% filter(year>2002)
table(find_rta$iso3_d, find_rta$rta_type, find_rta$year)
```


```{r}
count(unique(data_asean_selected$tradeflow_baci))
table(data_asean_selected$country_id_d, data_asean_selected$country_exists_d)
data_asean_selected %>% filter(iso3_d =="SGP")
```


