---
title: "Descriptive stats"
author: "Gaelle, Adele, Kateryna"
format: html
---

Countries (11): Brunei (BRN), Cambodia (KHM), Indonesia (IDN), Laos (LAO), Malaysia (MYS), Myanmar (MMR), Philippines (PHL), Singapore (SGP), Thailand (THA), Vietnam (VNM), Japan (JPN).

# General

```{r}
library(tidyverse)
library(fixest) # perform estimations with multiple fixed-effects
library(stargazer)
library(flextable)
library(huxtable)
```

# Data

```{r}
data_asean_raw <- read.csv("./Gravity_csv_V202211/Gravity_V202211.csv")
```

## Descriptive analysis

```{r}
#Code for 2000
 data_asean_description <- data_asean_raw %>%
     select(year, iso3_o, iso3_d, tradeflow_comtrade_d) %>%
     filter(year == 2000 & iso3_o %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM","JPN") & iso3_d %in% c("BRN","KHM","IDN","LAO","MYS","MMR","PHL","SGP","THA","VNM","JPN"))

plot_2000 <- ggplot(data_asean_description, aes(x = iso3_o, y = tradeflow_comtrade_d, fill = iso3_o)) +
     geom_bar(stat = "identity") +
     labs(title = "Trade Levels reported by the destination country for 10 ASEAN members countries in 2000",
          x = "Country", y = "Trade Level")

plot_2000

#Code for 2012
data_asean_description <- data_asean_raw %>%
     select(year, iso3_o, iso3_d, tradeflow_comtrade_d) %>%
     filter(year == 2012 & iso3_o %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM","JPN") & iso3_d %in% c("BRN","KHM","IDN","LAO","MYS","MMR","PHL","SGP","THA","VNM","JPN"))


plot_2012<- ggplot(data_asean_description, aes(x = iso3_o, y = tradeflow_comtrade_d, fill = iso3_o)) +
     geom_bar(stat = "identity") +
     labs(title = "Trade Levels reported by the destination country for 10 ASEAN members countries in 2012",
          x = "Country", y = "Trade Level")

grid.arrange(plot_2000, plot_2012, ncol = 2)
```


## General modifications

```{r}
#Select only countries and columns we need
#remove non-existing countries after they started existing in different form (+Singapore independence since 1965)
#remove tech variables
data_asean_selected <- data_asean_raw %>%
  select(c(year, country_id_o, country_id_d, iso3_o, iso3_d, country_exists_o, country_exists_d, dist, comlang_off, comlang_ethno, comcol, col45, comleg_pretrans, comleg_posttrans, comrelig, col_dep_end_conflict, gdp_o, gdp_d, gatt_o, gatt_d, wto_o, wto_d, rta_type, tradeflow_comtrade_d)) %>%
  filter(year >= 1965 & country_exists_o == 1 & country_exists_d == 1) %>%
  select(-c(country_id_o, country_id_d, country_exists_o, country_exists_d))
```

```{r}
#set rta_type and trade flows to 0 if NA
data_asean_selected <- data_asean_selected %>%
  mutate(rta_type = coalesce(rta_type, 0),
         tradeflow_comtrade_d = coalesce(tradeflow_comtrade_d, 0))
```

```{r}
#create new columns:
#general presence in either GATT or WTO by origin and destination
#general dummy for presence of any RTA for all countries
#dummy for presence in either GATT or WTO if both countries are members of it
data_asean_selected <- data_asean_selected %>%
  mutate(gatt_wto_o = case_when((gatt_o == 1 | wto_o == 1) ~ 1, TRUE ~ 0),
         gatt_wto_d = case_when((gatt_d == 1 | wto_d == 1) ~ 1, TRUE ~ 0),
         rta = if_else(rta_type == 0, 0, 1),
         .after = wto_d) %>%
  mutate(gatt_wto_both = if_else((gatt_wto_o == 1 & gatt_wto_d == 1), 1, 0))
```

## ASEAN specific modifications

```{r}
#create tech columns for 10 ASEAN member states by origin and destination
#and manually assign dummy 1 for ASEAN+1 agreement with Japan since 2008 (both general and directional for heterogeneity)
data_asean_selected <- data_asean_selected %>%
  mutate(asean_ms_o = case_when(iso3_o %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         asean_ms_d = case_when(iso3_d %in% c("BRN", "KHM", "IDN", "LAO", "MYS", "MMR", "PHL", "SGP", "THA", "VNM") ~ 1, TRUE ~ 0),
         rta_asean_plus = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN") | (year>=2008 & iso3_o=="JPN" & asean_ms_d==1) ~ 1, TRUE ~ 0),
         rta_asean_plus_a_j = case_when((year>=2008 & asean_ms_o==1 & iso3_d=="JPN" ~ 1), TRUE ~ 0),
         rta_asean_plus_j_a = case_when((year>=2008 & iso3_o=="JPN" & asean_ms_d==1 ~ 1), TRUE ~ 0))
```


## From section 4.1 with regressions
```{r}
# Select necessary years with 3 year intervals
asean_selected_rta <- data_asean_selected %>%
  filter(year %in% seq(1965, 2020, 3))
```

```{r}
# Construct symmetric pair id's for exporter and importer
asean_selected_rta <- asean_selected_rta %>%
  mutate(pair = paste(pmin(iso3_o,iso3_d),pmax(iso3_o,iso3_d),sep = "_")) %>%
  group_by(pair) %>%
  mutate(pair_id = cur_group_id())
```

```{r}
# calculate logs
asean_selected_rta <- asean_selected_rta %>%
  mutate(across(c(tradeflow_comtrade_d, dist, gdp_o, gdp_d), ~log(.x), .names="ln_{.col}"))
```

```{r}
#---create different columns for separating ASEAN dummy from general rta and rta_type -- needs to be set to 0 if manually created ASEAN dummy for Japan=1:

#adjust variables rta and rta_type by setting them to 0 if rta_asean_plus=1, so we don't duplicate when use both all RTA for RoW and specific Japan-ASEAN RTA in the regression
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta)),#general counterfactual
         rta_type_excl_asean_plus = if_else(rta_asean_plus==1, 0, as.numeric(rta_type))) #specific counterfactual

#based on adjusted rta_type segregate agreements of Japan in different types of RTA if Japan is in origin or destination
asean_selected_rta <- asean_selected_rta %>%
  mutate(jpn_cu = if_else((rta_type_excl_asean_plus==1 & iso3_o=="JPN") | (rta_type_excl_asean_plus==1 & iso3_d=="JPN"), 1, 0),
         jpn_cu_eia = if_else((rta_type_excl_asean_plus==2 & iso3_o=="JPN") | (rta_type_excl_asean_plus==2 & iso3_d=="JPN"), 1, 0),
         jpn_eia = if_else((rta_type_excl_asean_plus==3 & iso3_o=="JPN") | (rta_type_excl_asean_plus==3 & iso3_d=="JPN"), 1, 0),
         jpn_fta = if_else((rta_type_excl_asean_plus==4 & iso3_o=="JPN") | (rta_type_excl_asean_plus==4 & iso3_d=="JPN"), 1, 0),
         jpn_fta_eia = if_else((rta_type_excl_asean_plus==5 & iso3_o=="JPN") | (rta_type_excl_asean_plus==5 & iso3_d=="JPN"), 1, 0),
         jpn_psa_eia = if_else((rta_type_excl_asean_plus==7 & iso3_o=="JPN") | (rta_type_excl_asean_plus==7 & iso3_d=="JPN"), 1, 0))


#again adjust rta_type by setting them to 0 if member of ANY type of agreement is Japan,
#if not, then keep adjusted rta_type from the 1st step. This way we will not duplicate them in the regression when use variables specifically for Japan and for RoW (namely, when we use in regression Japan-ASEAN, Japan in all types of RTAs with RoW, and all types of RTAs between other countries in RoW)
asean_selected_rta <- asean_selected_rta %>%
  mutate(rta_type_all_clean = if_else((jpn_cu==1) | (jpn_cu_eia==1) | (jpn_eia==1) | (jpn_fta==1) | (jpn_fta_eia==1) | (jpn_psa_eia==1), 0, as.numeric(rta_type_excl_asean_plus)))
```

# Descriptive analysis

We will compare the situation of Japan between two years: 2000 when the negotiations of ASEAN+1 did not start yet and 2012, four years after the implementation of AJCEP.

```{r}
#Level of trade of Japan before and after AJCEP

```

